---
title: "Ontogeny of deep pelagic fish"
format: html
editor: visual
theme: minty
toc: true
toc-title: Sections
toc-location: left
page-layout: full
---

```{r}
#| echo: false
ontogeny_data <- utils::read.csv(here::here("data", "ontogeny.csv"), sep = ";", header = T,dec = ",")
ontogeny_data$species <- factor(ontogeny_data$species,
                               levels = c("Stomias_boa",
                                          "Lampanyctus_crocodilus",
                                          "Myctophum_punctatum",
                                          "Aphanopus_carbo",
                                          "Melanostigma_atlanticum",
                                          "Serrivomer_beanii",
                                          "Argyropelecus_olfersii",
                                          "Lampanyctus_macdonaldi",
                                          "Searsia_koefoedi",
                                          "Notoscopelus_kroyeri",
                                          "Xenodermichthys_copei",
                                          "Arctozenus_risso"),
                               labels = c("Stomias boa",
                                          "Lampanyctus crocodilus",
                                          "Myctophum punctatum",
                                          "Aphanopus carbo",
                                          "Melanostigma atlanticum",
                                          "Serrivomer beanii",
                                          "Argyropelecus olfersii",
                                          "Lampanyctus macdonaldi",
                                          "Searsia koefoedi",
                                          "Notoscopelus kroyeri",
                                          "Xenodermichthys copei",
                                          "Arctozenus risso"))
```

## $\delta$<sup>15</sup>N - size relationship

- significant relationships
- $\delta$<sup>15</sup>N axis standardized

```{r}
#| echo: false
#| warning: false
#| fig-height: 10
#| fig-width: 10

library(ggplot2)
ontogeny_significant <- subset(ontogeny_data, species=="Lampanyctus crocodilus"|
                                         species=="Aphanopus carbo"|
                                         species=="Melanostigma atlanticum" |
                                         species=="Serrivomer beanii"|
                                         species=="Stomias boa"|
                                         species=="Myctophum punctatum"|
                                         species=="Arctozenus risso")

ontogeny_significant$species <- factor(ontogeny_significant$species,
                               levels = c("Myctophum punctatum",
                                          "Melanostigma atlanticum",
                                          "Lampanyctus crocodilus",
                                          "Stomias boa",
                                          "Serrivomer beanii",
                                          "Aphanopus carbo",
                                          "Arctozenus risso"))

ggplot(ontogeny_significant , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.4, col="black") + 
  geom_smooth(method=lm, se=T, alpha=0.2, col= alpha("darkblue",0.7)) +
  facet_wrap(~species, scale="free_x", ncol=3)+ 
  ggpmisc::stat_poly_eq(formula = y ~ x, 
                        aes(label = paste(..eq.label.., ..rr.label.., ..p.value.label.. 
                                          , ..n.label..,sep = "*`,`~")),
                        parse = TRUE,
                        size=3,
                        label.x.npc = "right",
                        label.y.npc = "bottom",
                        vstep = -0.0005)+ 
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  ylim(c(7,13))+
  guides(color="none", fill="none")+
  theme_minimal()+
  theme(strip.text.x = element_text(size=10,face="italic"),
        axis.title = element_text(size=10),
        axis.text =  element_text(size=10))

```


- non significant relationships

```{r}
#| echo: false
#| warning: false
#| fig-height: 6
#| fig-width: 10
ontogeny_non_significant <- subset(ontogeny_data, species=="Argyropelecus olfersii"|
                                 species=="Lampanyctus macdonaldi"|
                                 species=="Searsia koefoedi" |
                                 species=="Notoscopelus kroyeri"|
                                 species=="Xenodermichthys copei")

ontogeny_non_significant$species <- factor(ontogeny_non_significant$species,
                                       levels = c("Argyropelecus olfersii",
                                                  "Lampanyctus macdonaldi",
                                                  "Searsia koefoedi",
                                                  "Notoscopelus kroyeri",
                                                  "Xenodermichthys copei"))

ggplot(ontogeny_non_significant , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.4, col="black") + 
  facet_wrap(~species, scale="free_x", ncol=3)+ 
  ggpmisc::stat_poly_eq(formula = y ~ x, 
                        aes(label = paste( ..n.label..,sep = "*`,`~")),
                        parse = TRUE,
                        size=3,
                        label.x.npc = "right",
                        label.y.npc = "bottom",
                        vstep = -0.0005)+ 
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  ylim(c(7,13))+
  guides(color="none", fill="none")+
  theme_minimal()+
  theme(strip.text.x = element_text(size=10,face="italic"),
        axis.title = element_text(size=10),
        axis.text =  element_text(size=10))

```


### Summarise results 
#### $\delta$<sup>15</sup>N size relationship
```{r}
#| echo: true
#| warning: false
library(tidyr)
library(dplyr)
ontogeny_d15n_size <- ontogeny_data %>%
  group_by(species) %>%
  do(broom::tidy(lm(d15N_muscle_untreated~size, data =.)))
DT::datatable(ontogeny_d15n_size)
```

#### $\delta$<sup>15</sup>N depth relationship
```{r}
#| echo: true
#| warning: false
ontogeny_d15n_depth <- ontogeny_data %>%
  group_by(species) %>%
  do(broom::tidy(lm(d15N_muscle_untreated~trawling_depth, data =.)))
DT::datatable(ontogeny_d15n_depth)
```

#### size depth relationship
```{r}
#| echo: true
#| warning: false
ontogeny_size_depth <- ontogeny_data %>%
  group_by(species) %>%
  do(broom::tidy(lm(size~trawling_depth, data =.)))
DT::datatable(ontogeny_size_depth)
```


### All relationship on 1 plot
```{r}
#| echo: false
#| warning: false 
#| fig-height: 6
#| fig-width: 10
ggplot(ontogeny_data , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.3, size=0.7, aes(col=species)) + 
  geom_smooth(method=lm, se=T, alpha=0.1, aes(col=species)) + 
  paletteer::scale_color_paletteer_d("ggsci::category20_d3")+
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  labs(col="Species")+
  guides(fill="none")+
  theme_minimal()+
  theme(axis.title = element_text(size=10),
        axis.text =  element_text(size=10),
        legend.text = element_text(face = "italic"))
```

### Significant relationship on 1 plot
_Arctozenus risso_ was the only species with a significantly negative relationship


```{r}
#| echo: false
#| warning: false 
#| fig-height: 6
#| fig-width: 10

ontogeny_significant <- subset(ontogeny_data, species=="Lampanyctus crocodilus"|
                                  species=="Aphanopus carbo"|
                                  species=="Melanostigma atlanticum"|
                                  species=="Serrivomer beanii"|
                                  species=="Stomias boa"|
                                  species=="Myctophum punctatum"|
                                  species=="Arctozenus risso")

ggplot(ontogeny_significant , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.3, size=0.7, aes(col=species)) + 
  geom_smooth(method=lm, se=T, alpha=0.1, aes(col=species)) + 
  paletteer::scale_color_paletteer_d("ggsci::category20_d3")+
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  labs(col="Species")+
  guides(fill="none")+
  theme_minimal()+
  theme(axis.title = element_text(size=10),
        axis.text =  element_text(size=10),
        legend.text = element_text(face = "italic"))
```

#### By separating large and small species
```{r}
#| echo: false
#| warning: false 
#| fig-height: 6
#| fig-width: 12

ontogeny_large_sp <- subset(ontogeny_data, species=="Aphanopus carbo"|
                                  species=="Serrivomer beanii"|
                                  species=="Stomias boa")

large_sp <- ggplot(ontogeny_large_sp , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.3, size=0.7, aes(col=species)) + 
  geom_smooth(method=lm, se=T, alpha=0.1, aes(col=species)) + 
  paletteer::scale_color_paletteer_d("ggsci::category20_d3")+
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  labs(col="Large species")+
  guides(fill="none")+
  ylim(c(7,13))+
  theme_minimal()+
  theme(axis.title = element_text(size=10),
        axis.text =  element_text(size=10),
        legend.text = element_text(face = "italic", size=10),
        legend.title = element_text(size=10),
        legend.position = c(0.7,0.1))


ontogeny_small_sp <- subset(ontogeny_data, species=="Lampanyctus crocodilus"|
                                  species=="Melanostigma atlanticum"|
                                  species=="Myctophum punctatum"|
                                  species=="Arctozenus risso")

small_sp <-ggplot(ontogeny_small_sp , aes(x=size, y=d15N_muscle_untreated))+
  geom_point (alpha=0.3, size=0.7, aes(col=species)) + 
  geom_smooth(method=lm, se=T, alpha=0.1, aes(col=species)) + 
  paletteer::scale_color_paletteer_d("ggsci::category20_d3")+
  xlab("Standard Length (cm)")+
  ylab(expression({delta}^15*N~'\u2030'))+
  labs(col="Small species")+
  guides(fill="none")+
  theme_minimal()+
  ylim(c(7,13))+
  theme(axis.title = element_text(size=10),
        axis.text =  element_text(size=10),
        legend.text = element_text(face = "italic", size=10),
        legend.title = element_text(size=10),
        legend.position = c(0.7,0.1))

gridExtra::grid.arrange(large_sp,small_sp, ncol=2)
```


# Size in function of depth 
## density plot 
-> data from the sampled individuals  
-> binwidth = 1cm

results of linear models (lm(size~trawling_depth)):  

- significantly positive relationships: _M. atlanticum, L. crocodilus, N. kroyeri, M. punctatum_  
- significantly negative relationships: _A. risso, X. copei_  
- non-significant relationships: _S. beanii, A. olfersii, S. koefoedi, L. macdonaldi_ (small size range), _A. carbo_ (small depth range), _S. boa_ (small depth range)

```{r}
#| echo: false
#| warning: false 
#| fig-height: 13
#| fig-width: 20

ontogeny_data_density <- ontogeny_data
ontogeny_data_density$depth_layer <- factor(ontogeny_data_density$depth_layer, 
                                  levels = c("epipelagic","upper_mesopelagic",
                                         "lower_mesopelagic","bathypelagic"),
                                  labels = c("Epipelagic","Upper mesopelagic",
                                          "Lower mesopelagic","Bathypelagic"))

ontogeny_data_density$species <- factor(ontogeny_data_density$species,
                                                   levels = c("Melanostigma atlanticum",
                                                               "Lampanyctus crocodilus",
                                                              "Notoscopelus kroyeri",
                                                              "Myctophum punctatum",
                                                              "Arctozenus risso",
                                                              "Xenodermichthys copei",
                                                              "Serrivomer beanii",
                                                              "Argyropelecus olfersii",
                                                              "Searsia koefoedi",
                                                               "Lampanyctus macdonaldi",
                                                              "Aphanopus carbo",
                                                              "Stomias boa"),
                                        labels = c("M.atlanticum",
                                                               "L.crocodilus",
                                                              "N.kroyeri",
                                                              "M.punctatum",
                                                              "A.risso",
                                                              "X.copei",
                                                              "S.beanii",
                                                              "A.olfersii",
                                                              "S.koefoedi",
                                                               "L.macdonaldi",
                                                              "A.carbo",
                                                              "S.boa"))

# df2 <- ontogeny_data %>%
#   group_by(species, depth_layer) %>%
#   summarise(Mean.SL = mean(size))

ggplot(ontogeny_data_density, aes(x=size)) +
  geom_density(alpha=0.3, aes(col=depth_layer), linewidth=0.7)+
  geom_histogram(aes(y=..density.., col=depth_layer, fill=depth_layer), alpha=0.2, 
                 position="identity", binwidth = 1)+
  facet_grid(depth_layer~species, scale="free")+
  theme_minimal()+
  theme(strip.text.x = element_text(size=16,face="italic"),
        strip.text.y = element_text(size=17),
        axis.title = element_text(size=19),
        axis.text =  element_text(size=14, color= "grey50"),
        panel.background=element_rect(color="white"),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14))+
 # geom_vline(data = df2, mapping = aes(xintercept = Mean.SL)) +
  guides(fill="none",col="none")+
  xlab("Standard Length (cm)")
```


# Variation partitioning _vs_ SEM

__Varpart (cf workshop QCBS) :__ 

- The fraction between size and depth (overlap between the two circles) does not represent the interaction between the two variables (it is the part of the variance that cannot be attributed to depth or size separately)

- Therefore, we cannot test the significance of this relationship

## _Lampanyctus crocodilus_ 

```{r}
#| echo: false
#| warning: false

m2 <- 'd15N ~ Depth + Size 
Depth~Size'
# m2 <- 'd15N ~ Profondeur + Size'

#labels 
lbls <- c(expression({delta}^15*N),"Depth","Size")
```

```{r}
#| echo: true
#| warning: false 
#| fig-height: 5
#| fig-width: 5

#Varpart
lamp_cro <- subset (ontogeny_data, ontogeny_data$species == "Lampanyctus crocodilus")
lamp_cro_part <- vegan::varpart(lamp_cro$d15N_muscle_untreated,
                            ~trawling_depth, ~size, data =lamp_cro)
lamp_cro_part$part

plot(lamp_cro_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
lamp_cro_scale <- as.data.frame(cbind(scale(lamp_cro$trawling_depth), 
                  scale(lamp_cro$d15N_muscle_untreated), 
                  scale(lamp_cro$size)))

colnames(lamp_cro_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=lamp_cro_scale)
lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)

```


## _Myctophum punctatum_

- SEM: depth-size significant & d15N-depth non significant 
- varpart: the opposite
```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
myct_pun <- subset(ontogeny_data, ontogeny_data$species == "Myctophum punctatum")
myct_pun_part <- vegan::varpart(myct_pun$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data =myct_pun)
plot(myct_pun_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # color the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
myct_pun_scale <- as.data.frame(cbind(scale(myct_pun$trawling_depth), 
                  scale(myct_pun$d15N_muscle_untreated), 
                  scale(myct_pun$size)))

colnames(myct_pun_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=myct_pun_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Melanostigma atlanticum_ 

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
mela_atl <- subset(ontogeny_data, ontogeny_data$species == "Melanostigma atlanticum")
mela_atl_part <- vegan::varpart(mela_atl$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = mela_atl)
plot(mela_atl_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
mela_atl_scale <- as.data.frame(cbind(scale(mela_atl$trawling_depth), 
                  scale(mela_atl$d15N_muscle_untreated), 
                  scale(mela_atl$size)))

colnames(mela_atl_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=mela_atl_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Serrivomer beanii_
```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
serr_bea <- subset(ontogeny_data, ontogeny_data$species == "Serrivomer beanii")
serr_bea_part <- vegan::varpart(serr_bea$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = serr_bea)
plot(serr_bea_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
serr_bea_scale <- as.data.frame(cbind(scale(serr_bea$trawling_depth), 
                  scale(serr_bea$d15N_muscle_untreated), 
                  scale(serr_bea$size)))

colnames(serr_bea_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=serr_bea_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Argyropelecus olfersii_

```{r}
#| echo: false
#| warning: false
#| #| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
argy_olf <- subset(ontogeny_data, ontogeny_data$species == "Argyropelecus olfersii")
argy_olf_part <- vegan::varpart(argy_olf$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = argy_olf)
plot(argy_olf_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
argy_olf_scale <- as.data.frame(cbind(scale(argy_olf$trawling_depth), 
                  scale(argy_olf$d15N_muscle_untreated), 
                  scale(argy_olf$size)))

colnames(argy_olf_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=argy_olf_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Lampanyctus macdonaldi_

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
lamp_mac <- subset(ontogeny_data, ontogeny_data$species == "Lampanyctus macdonaldi")
lamp_mac_part <- vegan::varpart(lamp_mac$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = lamp_mac)
plot(lamp_mac_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
lamp_mac_scale <- as.data.frame(cbind(scale(lamp_mac$trawling_depth), 
                  scale(lamp_mac$d15N_muscle_untreated), 
                  scale(lamp_mac$size)))

colnames(lamp_mac_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=lamp_mac_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```

## _Searsia koefoedi_

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
sear_koe <- subset(ontogeny_data, ontogeny_data$species == "Searsia koefoedi")
sear_koe_part <- vegan::varpart(sear_koe$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = sear_koe)
plot(sear_koe_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
sear_koe_scale <- as.data.frame(cbind(scale(sear_koe$trawling_depth), 
                  scale(sear_koe$d15N_muscle_untreated), 
                  scale(sear_koe$size)))

colnames(sear_koe_scale)<- c("Depth","d15N","Size")

fit2 <- lavaan::sem(m2, data=sear_koe_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Notoscopelus kroyeri_

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
noto_kro <- subset(ontogeny_data, ontogeny_data$species == "Notoscopelus kroyeri")
noto_kro_part <- vegan::varpart(noto_kro$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = noto_kro)
plot(noto_kro_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
noto_kro_scale <- as.data.frame(cbind(scale(noto_kro$trawling_depth), 
                  scale(noto_kro$d15N_muscle_untreated), 
                  scale(noto_kro$size)))

colnames(noto_kro_scale)<- c("Depth","d15N","Size")
fit2 <- lavaan::sem(m2, data=noto_kro_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Xenodermichthys copei_

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
xeno_cop <- subset(ontogeny_data, ontogeny_data$species == "Xenodermichthys copei")
xeno_cop_part <- vegan::varpart(xeno_cop$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = xeno_cop)
plot(xeno_cop_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
xeno_cop_scale <- as.data.frame(cbind(scale(xeno_cop$trawling_depth), 
                  scale(xeno_cop$d15N_muscle_untreated), 
                  scale(xeno_cop$size)))

colnames(xeno_cop_scale)<- c("Depth","d15N","Size")
fit2 <- lavaan::sem(m2, data=xeno_cop_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


## _Arctozenus risso_

```{r}
#| echo: false
#| warning: false
#| fig-height: 7
#| fig-width: 13
par(mfrow= c(1,2))

#Varpart
arct_ris <- subset(ontogeny_data, ontogeny_data$species == "Arctozenus risso")
arct_ris_part <- vegan::varpart(arct_ris$d15N_muscle_untreated,
                                ~trawling_depth, ~size, data = arct_ris)
plot(arct_ris_part,
     Xnames = c("Depth", "size"), # name the partitions
     bg = c("#072AC8", "#0B5345"), alpha = 100, # colour the circles
     digits = 2, # only show 2 digits
     cex = 1.4)

#SEM
arct_ris_scale <- as.data.frame(cbind(scale(arct_ris$trawling_depth), 
                  scale(arct_ris$d15N_muscle_untreated), 
                  scale(arct_ris$size)))

colnames(arct_ris_scale)<- c("Depth","d15N","Size")
fit2 <- lavaan::sem(m2, data=arct_ris_scale)
#lavaan::summary(fit2)
semPlot::semPaths(fit2, "par", residuals = F,nodeLabels = lbls, edge.label.cex = 2, 
         fade=F, posCol="#3B9152", sizeMan = 12)
```


```{r}
#| echo: false
#| warning: false 
## For all species at once 
ontogeny_summary <- ontogeny_data %>%
  group_by(species) %>%
  summarise(vegan::varpart(ontogeny_data$d15N_muscle_untreated,
                         ~trawling_depth, ~size, data =.)) 
```

# Classification
- classification according to the slope coefficients of the different relationships (set a different value for non-significant relationships?)
- 1 model (lm) performed /relationship/species
```{r}
#| echo: true
#| warning: false
#| fig-height: 4
#| fig-width: 9

slope_data <- utils::read.csv(here::here("data", "slope_coefficients.csv"),
                              sep = ";", h=T, row.names=1, dec =",", check.names = F)

slope_veg <- vegan::vegdist(slope_data, method = "jaccard", binary=FALSE)
ggdendro::ggdendrogram(hclust(slope_veg, "ward.D2"), rotate = FALSE)
```
- group 1 : species with negative relationship __size-depth__
- group 2 : species with positive relationship __$\delta$<sup>15</sup>N-size__ & __size-depth__
- group 3 : species with no significant relationship (except _A.olfersii_ __$\delta$<sup>15</sup>N-depth__)
- group 4 : species with 1 significant relationship ( _S.beanii_ __$\delta$<sup>15</sup>N-depth__ & _N.kroyeri_ __size-depth__) 

# Figures et graphiques à inclure dans le papier dans l'ordre : 

- carte d'échantillonnage 

- Tableau résumé de l'échantillonnage (familles, espèces, N, type de migration, range de taille et de profondeur, taille max fishbase et moyenne des valeurs de $\delta$<sup>15</sup>N avec SD)

- plot relations $\delta$<sup>15</sup>N-taille /sp (significatives + non significatives)

- plot relation $\delta$<sup>15</sup>N-taille significatives sur le même plot 

- density plot/histogramme de la taille en fonction de la profondeur /sp: mieux d'ulitser que les données des individus prélevés (et pas la série complète) pour éviter les confusions ? 

- Modèles /sp : SEM vs Varpart ? autre à tester ? (intéressant de prendre en compte le lien entre la distribution en taille des individus et la profondeur)

- Tableau récapitulatif des résultats de significativité des modèles ? 

- Cluster : quelles données d'entrée ? coefficient des modèles lm ou SEM ou Varpart ? 

# Supplementary material
## Distribution en taille des espèces (individus échantillonnés)
```{r}
#| echo: false
#| warning: false 
#| fig-height: 9
#| fig-width: 14

ggplot(ontogeny_data, aes(x=size)) +
  geom_density(alpha=0.2, linewidth=0.7, col= "darkblue", fill= "darkblue")+
  facet_wrap(~species, scale="free")+
  theme_minimal()+
  theme(strip.text.x = element_text(size=16,face="italic"),
        strip.text.y = element_text(size=17),
        axis.title = element_text(size=19),
        axis.text =  element_text(size=14, color= "grey50"),
        panel.background=element_rect(color="white"),
        legend.title = element_text(size=14),
        legend.text = element_text(size=14))+
 # geom_vline(data = df2, mapping = aes(xintercept = Mean.SL)) +
  guides(fill="none",col="none")+
  xlab("Standard Length (cm)")
```

## Echantillonnage en fonction des années 
- Plus de 90% de l'échantillonnage a été effectué entre 2019 et 2021 (et presque les 3/4 en 2021)
```{r}
#| echo: false
#| warning: false 
#| fig-height: 11
#| fig-width: 21

ontogeny_data$years <- as.character(ontogeny_data$years)
ggplot(ontogeny_data, aes(x=years, y=d15N_muscle_untreated, col=trawling_depth,
                     group=years))+
  geom_point (alpha=0.5, size=2.5) +
  geom_boxplot(fill="grey", col="grey", alpha=0.2)+
  facet_wrap(~species, scale="free")+ 
  xlab("Years")+
  scale_color_gradient(low = "blue", high = "darkorange")+
  ylab(expression({delta}^15*N~'\u2030'))+
  guides(fill="none")+
  theme_minimal()+
  theme(strip.text.x = element_text(size=18,face="italic"),
        axis.title = element_text(size=18),
        axis.text =  element_text(size=18),
        legend.title = element_text(size=18),
        legend.text = element_text(size=18))+
  labs(col="Depth (m)")
```
# Plan intro

__1. Importance of deep-pelagic fish in food webs__

- different roles : consummation of zooplankton, source of prey for top predators and benthic/demersal speices  

- Therefore, better understand their trophic ecology is essential to quantified their role in the functioning of the ecosystem and the services ecosystem they provide... 

__2. Use of stable isotope to characterized their trophic ecology__ 

- Description of the use of $\delta$<sup>15</sup>N values in trophic ecology

__3.	However, trophic ecology of deep-pelagic fish is challenging to study__ 

- Variations in $\delta$<sup>15</sup>N values due to the environment: microbial degradation ...

- In addition, meso- and bathypelagic fish exhibit large variety of feeding patterns adding a level of complexity : migratory behavior, ontogenetic changes in diet, ontogenetic shift in vertical distribution, link with the bottom

__4. Therefore, use of (path) models ...__ 
